---
title: "My .Rprofile"
knit: customiser::customiser
---

This is the file I use for compiling my .Rprofile.

# Strategy

Creating a personalised .RProfile involves balancing two competing concerns.
The first is the desire for customisation. You want functionality to be 
automatically available to you in every R session that you create. But you
also want a clean R environment. This is perhaps most difficult when relying 
on external packages. You don't want to load them, even using `::`. One reason 
is that they might affect installs.

One way to tackle this is to wrap a lot of functionality in functions. Which 
(basically) don't have any effect until they are called.

# Helpers

For creating helper functions in an environment. Then attaching at the end of
the script.

```{r}
.e <- new.env()
```


Am I at work?

```{r}
.e$at_work <- function() {
  if(Sys.info()["user"] == "jameslaird-smith") return(FALSE)
  TRUE
}

.e$my_email <- function() {
  if(.e$at_work()) return("James.Laird-Smith@bankofengland.co.uk")
  "jameslairdsmith@gmail.com"
}
```

Am I using RStudio?

Strangely, this is the best way I've found to do this, among many worse 
[alternatives](https://twitter.com/JLS_DataScience/status/1587904642670804993?s=20&t=tTPjcXTZW61NZS7fuYDDhQ)

```{r}
.e$on_rstudio <- function() {
  if (commandArgs()[[1L]] == "RStudio") {
    return(TRUE)
  }
  FALSE
}
```

# General preferences

```{r}
options(max.print = 40)
options(connectionObserver = NULL)
# ^ connectionObserver at work just gets in the way.
```


# Package dev

```{r}
options(
  usethis.full_name = "James Laird-Smith",
  usethis.description = list(
    "Authors@R" = utils::person(
      "James", "Laird-Smith",
      email = .e$my_email(),
      role = c("aut", "cre"),
      comment = c(ORCID = "0000-0003-1175-4046")
    ),
    Version = "0.0.0.9000"
  ),
  usethis.overwrite = TRUE
)
```


# RStudio 

## Preferences

```{r}
setHook("rstudio.sessionInit", function(newSession) {
  rstudioapi::writeRStudioPreference("editor_keybindings", "vim")
  rstudioapi::writeRStudioPreference("save_workspace", "never")
  rstudioapi::writeRStudioPreference("always_save_history", FALSE)
  rstudioapi::writeRStudioPreference("save_files_before_build", TRUE)
}, action = "append")
```

## Keyboard shortcuts

List of all available RStudio Commands: https://docs.rstudio.com/ide/server-pro/1.3.1007-2/rstudio-ide-commands.html

Actually, this might be better: https://docs.rstudio.com/ide/server-pro/rstudio_ide_commands/rstudio_ide_commands.html

```{r}
if (.e$on_rstudio() & interactive() & requireNamespace("shrtcts", quietly = TRUE)) {
  shrtcts::add_rstudio_shortcuts(set_keyboard_shortcuts = TRUE)
}
```

My keyboard shortcuts are very hyper-key dependent at the moment, because I've
programmed my keyboard to make that easy. But it's not workable when I don't 
have my programmable keyboard, so might require rethinking soon.

# Prompt

I really like it when the prompt captures how long the previous operation has
taken.

```{r}
if (requireNamespace("prompt", quietly = TRUE)) {
  prompt::set_prompt(function(...) paste0(prompt::prompt_runtime()))
}
```


# Linting and styling

```{r}
options(styler.cache_root = "styler-perm")
```

# Final actions

Attach shortcuts.

```{r}
attach(.e)
```


