---
title: "JLS .Rprofile"
knit: customiser::customiser
allow_overwrite: TRUE
---

This is the file I use for compiling my .Rprofile.

# Strategy

Creating a personalised .RProfile involves balancing two competing concerns.
The first is the desire for customisation. You want functionality to be 
automatically available to you in every R session that you create. But you
also want a clean R environment. This is perhaps most difficult when relying 
on external packages. You don't want to load them, even using `::`. One reason 
is that they might affect installs.

One way to tackle this is to wrap a lot of customisation in functions. Which 
have far fewer effects unit they are called.

# Helpers

For creating helper functions in an environment. Then attaching at the end of
the script.

```{r}
jls <- new.env()
```

Am I at work?

```{r}
at_work <- function() {
  if(Sys.info()["user"] == "jameslaird-smith") return(FALSE)
  TRUE
}

my_email <- function() {
  if(at_work()) return("James.Laird-Smith@bankofengland.co.uk")
  "jameslairdsmith@gmail.com"
}
```

Am I using RStudio?

Strangely, this is the best way I've found to do this, among many worse 
[alternatives](https://twitter.com/JLS_DataScience/status/1587904642670804993?s=20&t=tTPjcXTZW61NZS7fuYDDhQ)

```{r}
on_rstudio <- function() {
  if (commandArgs()[[1L]] == "RStudio") {
    return(TRUE)
  }
  FALSE
}
```

# General preferences

```{r}
options(max.print = 40)
options(connectionObserver = NULL)
# ^ connectionObserver at work just gets in the way.
options(tidyverse.quiet = TRUE)
# ^ Is there a way to silence S3 overwrites?
```

It also might be good to set `_R_S3_METHOD_REGISTRATION_NOTE_OVERWRITES_`?

# Repos

If I'm not at work, I just using the default that RStudio would use even if
I'm not in RStudio.

```{r}
if(!at_work()) {
  options(repos = c(CRAN='https://cloud.r-project.org'))
}
```

If I am at work, then these values get set separately.

# Package dev

```{r}
options(
  usethis.full_name = "James Laird-Smith",
  usethis.description = list(
    "Authors@R" = utils::person(
      "James", "Laird-Smith",
      email = my_email(),
      role = c("aut", "cre"),
      comment = c(ORCID = "0000-0003-1175-4046")
    ),
    Version = "0.0.0.9000"
  ),
  usethis.overwrite = TRUE
)
```


# Python dev

I'm not sure why this was being set in my MacOS config, but explicitly setting
it makes it fine.

```{r}
if(!at_work){
  Sys.setenv(RETICULATE_PYTHON="/usr/local/bin/python3")
}
```

# RStudio 

## Preferences

```{r}
setHook("rstudio.sessionInit", function(newSession) {
  rstudioapi::writeRStudioPreference("editor_keybindings", "vim")
  rstudioapi::writeRStudioPreference("save_workspace", "never")
  rstudioapi::writeRStudioPreference("always_save_history", FALSE)
  rstudioapi::writeRStudioPreference("save_files_before_build", TRUE)
  # rstudioapi::applyTheme("Kr Theme") # This doesn't seem to work so well
}, action = "append")
```

## Keyboard shortcuts

List of all available RStudio Commands: https://docs.rstudio.com/ide/server-pro/1.3.1007-2/rstudio-ide-commands.html

Actually, this might be better: https://docs.rstudio.com/ide/server-pro/rstudio_ide_commands/rstudio_ide_commands.html

```{r}
jls$jls_set_shrtcts <- function() {
  shrtcts::add_rstudio_shortcuts(set_keyboard_shortcuts = TRUE)
}
```

My keyboard shortcuts are very hyper-key dependent at the moment, because I've
programmed my keyboard to make that easy. But it's not workable when I don't 
have my programmable keyboard, so might require rethinking soon.

# Prompt

I really like it when the prompt captures how long the previous operation has
taken.

```{r}
# if (requireNamespace("prompt", quietly = TRUE)) {
#   prompt::set_prompt(function(...) paste0(prompt::prompt_runtime()))
# }
```

But maybe I won't use that right now. Just a lambda, to be like the cool kids.

```{r}
options(prompt = "\u03BB > ")
```


# Linting and styling

```{r}
options(styler.cache_root = "styler-perm")
```

# Final actions

Attach shortcuts.

TODO: make it the last thing that is attached.

```{r}
attach(jls)
```

Cleanup

Removing the helpers that I created before.

```{r}
rm(at_work, my_email, on_rstudio, jls)
```
